The Hydrogen Epoch of Reionization Array Dish I: Beam Pattern Measurements and Science Implications

### 2016-02-10 DishBeamMeasurements/paper/DishBeamMeasurementsPaper_rev2.tex

\author{Abraham R. Neben\altaffilmark{1},
Richard F. Bradley\altaffilmark{2,3},
Aaron Ewall-Wice\altaffilmark{1},
Nipanjana Patra\altaffilmark{4},
Nithyanandan Thyagarajan\altaffilmark{5},
James E. Aguirre\altaffilmark{6},
Zaki S. Ali\altaffilmark{4},
Judd Bowman\altaffilmark{5}
Carina Cheng\altaffilmark{4},
David R. DeBoer\altaffilmark{4}
Jacqueline N. Hewitt\altaffilmark{1},
Aaron Parsons\altaffilmark{4}}

@@

\begin{abstract}
The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral Hydrogen from the Epoch of Reionization. Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$. This is the first of a series of four papers characterizing the frequency and angular response of the HERA dish element with simulations and measurements. In this work we measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}. We measure collecting areas of 70--100\,m$^2$ and predict power spectrum SNRs. With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with a signal-to-noise of 25--30 with a single season of observations. Even pessimistically assuming that only previously demonstrated techniques are used, the significance of an EOR detection remains above $5\sigma$. Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
\end{abstract}

@@

\begin{figure}[h]
\includegraphics[width=3.4in]{IMG_0353.JPG}
\caption{The dish with its suspended feed is seen in the back, 50\,m north of one of the reference antennas used in the null experiment to study systematics. The experiment is conducted in Galford Meadow at NRAO--Green Bank.}
\label{fig:greenbankdishphoto}
\end{figure}

>>>>

\author{Abraham R. Neben\altaffilmark{1},
Richard F. Bradley\altaffilmark{2,3},
Aaron Parsons\altaffilmark{4},
Jacqueline N. Hewitt\altaffilmark{1},
David R. DeBoer\altaffilmark{4}
Aaron Ewall-Wice\altaffilmark{1},
Nipanjana Patra\altaffilmark{4},
Nithyanandan Thyagarajan\altaffilmark{5},
James E. Aguirre\altaffilmark{6},
Zaki S. Ali\altaffilmark{4},
Judd Bowman\altaffilmark{5},
Carina Cheng\altaffilmark{4}}

@@

\begin{abstract}
The Hydrogen Epoch of Reionization Array (HERA) is a radio interferometer aiming to detect the power spectrum of 21\,cm fluctuations from neutral Hydrogen from the Epoch of Reionization. Drawing on lessons from the Murchison Widefield Array (MWA) and the Precision Array for Probing the Epoch of Reionization (PAPER), HERA is a hexagonal array of large (14\,m) dishes with suspended dipole feeds with element collecting area of 100\,m$^2$. This is the first of a series of four papers characterizing the frequency and angular response of the HERA dish element with simulations and measurements. In this work we measure the angular response at 137\,MHz using the ORBCOMM beam mapping system of \citet{neben15}. We measure collecting areas of 70--100\,m$^2$ and predict power spectrum SNRs. With optimistic foreground and analysis assumptions, HERA-127 should detect the EOR with a signal-to-noise of 25--30 with a single season of observations. Even with more pessimistic assumptions, using only previously demonstrated techniques, the significance of an EOR detection remains above $5\sigma$. Lastly we simulate foreground visibilities using numerical beam models and study the foreground distribution in Fourier space as a function of LST, and the uncertainties in these predictions due to beam modeling uncertainties.
\end{abstract}

@@

\begin{figure}[h]
\includegraphics[width=3.4in]{ref_dipole_and_hera_dish.jpg}
\caption{The dish with its suspended feed is seen in the back, 50\,m north of one of the reference antennas used in the null experiment to study systematics. The experiment is conducted in Galford Meadow at NRAO--Green Bank.}
\label{fig:greenbankdishphoto}
\end{figure}
